%_____________________________________________________________________________________________ 
% LATEX Template: Department of Comp/IT BTech Project Reports
% Abstract of Report
%_____________________________________________________________________________________________ 
\newpage
%\begin{abstract}
%\addcontentsline{toc}{chapter}{Abstract}	% This makes sure abstract is included in contents.
\begin{center}
\Large \textbf{Abstract}
\end{center}
Time table generation is a time consuming problem faced by many educational institutes. It belongs to the class of combinatorial optimization problems. We have implemented a semi-automated approach for solving this constraint heavy problem for educational institutes like College of Engineering Pune (COEP). It allows the user to make time table as per his/her choice while ensuring all constraints are satisfied and there are no conflicts. There are some existing solutions for this problem which are fully automated but difficult to use. We adopted a much simpler approach for solving it. We have developed a desktop application using object oriented programming paradigm with a user friendly interface. \par
It supports quantification of constraints, importing data from text files, mapping and filtering of data. Basic features such as cut, copy, paste are available. One can merge, unmerge no of cells as per requirements. Venue utilisation statistics and global warnings are readily available. Keyboard shortcuts are available for frequently used functions. Timetable can be exported in pdf, html and ods formats. \par
The code is available on GitHub under General Public License (GPLv3). 
\\\texttt{https://github.com/Aadesh-Magare/Btech-Project-Timetable-Management}
%\end{abstract}

%_____________________________________________________________________________________________ 
